Draft Final Report: Measles risk assessment, modelling, and benefit--cost analyses for New Zealand

### 2015-03-21 draftfinalreport_v2.tex
Tidying and revisions
Eg relevel for the regression

\begin{table}[hbtp]\scriptsize
%latex.default(ttyr, file = "", table.env = FALSE, rowname = NULL)%
\begin{center}
\begin{tabular}{lllrl}
\hline\hline
\multicolumn{1}{c}{NZDep}&\multicolumn{1}{c}{Age}&\multicolumn{1}{c}{Ethnicity}&\multicolumn{1}{c}{Cases}&\multicolumn{1}{c}{merge}\tabularnewline
\hline
1-3&0-1&Asian&$  6$&1-3 0-1 Asian\tabularnewline
4-7&0-1&Asian&$ 10$&4-7 0-1 Asian\tabularnewline
8-10&0-1&Asian&$  3$&8-10 0-1 Asian\tabularnewline
1-3&2-4&Asian&$  1$&1-3 2-4 Asian\tabularnewline
1-3&5-17&Asian&$  6$&1-3 5-17 Asian\tabularnewline
4-7&5-17&Asian&$  8$&4-7 5-17 Asian\tabularnewline
8-10&5-17&Asian&$  2$&8-10 5-17 Asian\tabularnewline
1-3&18-24&Asian&$  2$&1-3 18-24 Asian\tabularnewline
4-7&18-24&Asian&$  3$&4-7 18-24 Asian\tabularnewline
8-10&18-24&Asian&$  3$&8-10 18-24 Asian\tabularnewline
1-3&25+&Asian&$  4$&1-3 25+ Asian\tabularnewline
4-7&25+&Asian&$ 11$&4-7 25+ Asian\tabularnewline
8-10&25+&Asian&$  8$&8-10 25+ Asian\tabularnewline
1-3&0-1&European&$ 40$&1-3 0-1 European\tabularnewline
4-7&0-1&European&$ 58$&4-7 0-1 European\tabularnewline
8-10&0-1&European&$ 24$&8-10 0-1 European\tabularnewline
1-3&2-4&European&$ 37$&1-3 2-4 European\tabularnewline
4-7&2-4&European&$ 22$&4-7 2-4 European\tabularnewline
8-10&2-4&European&$  6$&8-10 2-4 European\tabularnewline
1-3&5-17&European&$160$&1-3 5-17 European\tabularnewline
4-7&5-17&European&$118$&4-7 5-17 European\tabularnewline
8-10&5-17&European&$ 40$&8-10 5-17 European\tabularnewline
1-3&18-24&European&$ 24$&1-3 18-24 European\tabularnewline
4-7&18-24&European&$ 26$&4-7 18-24 European\tabularnewline
8-10&18-24&European&$ 20$&8-10 18-24 European\tabularnewline
1-3&25+&European&$ 54$&1-3 25+ European\tabularnewline
4-7&25+&European&$ 46$&4-7 25+ European\tabularnewline
8-10&25+&European&$ 29$&8-10 25+ European\tabularnewline
1-3&0-1&Maori&$  9$&1-3 0-1 Maori\tabularnewline
4-7&0-1&Maori&$ 13$&4-7 0-1 Maori\tabularnewline
8-10&0-1&Maori&$ 32$&8-10 0-1 Maori\tabularnewline
1-3&2-4&Maori&$  4$&1-3 2-4 Maori\tabularnewline
4-7&2-4&Maori&$ 12$&4-7 2-4 Maori\tabularnewline
8-10&2-4&Maori&$ 10$&8-10 2-4 Maori\tabularnewline
1-3&5-17&Maori&$  8$&1-3 5-17 Maori\tabularnewline
4-7&5-17&Maori&$ 33$&4-7 5-17 Maori\tabularnewline
8-10&5-17&Maori&$ 74$&8-10 5-17 Maori\tabularnewline
1-3&18-24&Maori&$  3$&1-3 18-24 Maori\tabularnewline
4-7&18-24&Maori&$  2$&4-7 18-24 Maori\tabularnewline
8-10&18-24&Maori&$  8$&8-10 18-24 Maori\tabularnewline
1-3&25+&Maori&$  1$&1-3 25+ Maori\tabularnewline
4-7&25+&Maori&$  3$&4-7 25+ Maori\tabularnewline
8-10&25+&Maori&$  4$&8-10 25+ Maori\tabularnewline
4-7&0-1&MLA&$  2$&4-7 0-1 MLA\tabularnewline
8-10&0-1&MLA&$  1$&8-10 0-1 MLA\tabularnewline
8-10&2-4&MLA&$  1$&8-10 2-4 MLA\tabularnewline
8-10&5-17&MLA&$  1$&8-10 5-17 MLA\tabularnewline
8-10&18-24&MLA&$  2$&8-10 18-24 MLA\tabularnewline
4-7&25+&MLA&$  5$&4-7 25+ MLA\tabularnewline
8-10&25+&MLA&$  1$&8-10 25+ MLA\tabularnewline
1-3&0-1&Pacific&$  1$&1-3 0-1 Pacific\tabularnewline
4-7&0-1&Pacific&$  6$&4-7 0-1 Pacific\tabularnewline
8-10&0-1&Pacific&$ 48$&8-10 0-1 Pacific\tabularnewline
4-7&2-4&Pacific&$  1$&4-7 2-4 Pacific\tabularnewline
8-10&2-4&Pacific&$ 10$&8-10 2-4 Pacific\tabularnewline
1-3&5-17&Pacific&$  2$&1-3 5-17 Pacific\tabularnewline
4-7&5-17&Pacific&$  4$&4-7 5-17 Pacific\tabularnewline
8-10&5-17&Pacific&$ 21$&8-10 5-17 Pacific\tabularnewline
4-7&18-24&Pacific&$  4$&4-7 18-24 Pacific\tabularnewline
8-10&18-24&Pacific&$  5$&8-10 18-24 Pacific\tabularnewline
1-3&25+&Pacific&$  1$&1-3 25+ Pacific\tabularnewline
4-7&25+&Pacific&$  3$&4-7 25+ Pacific\tabularnewline
8-10&25+&Pacific&$  9$&8-10 25+ Pacific\tabularnewline
\hline
\end{tabular}\end{center}\caption{Absolute number of measles cases with no ethnicity recorded for specific age and socio-economic deprivation (NZDep) categories from 2007-2014.}
\label{table:none}
\end{table}

@@

\begin{table}[hbtp]\scriptsize
\caption{Per capita measles rates}
\end{tabular}\end{center}\label{table:percap_rates}

\begin{table}[hbtp]\footnotesize
\caption{Proportions of the naive population the would be covered if vaccinated by age groups}
%latex.default(propvCohort, file = "", table.env = FALSE)%
\begin{center}
\begin{tabular}{lr}
\hline\hline
\multicolumn{1}{l}{propvCohort}&\multicolumn{1}{c}{}\tabularnewline
\hline
2-5&$0.04$\tabularnewline
5-11&$0.15$\tabularnewline
5-16&$0.27$\tabularnewline
5-18&$0.31$\tabularnewline
11-16&$0.14$\tabularnewline
11-18&$0.18$\tabularnewline
0-29&$0.72$\tabularnewline
0-44&$0.89$\tabularnewline
\textgreater 8&$0.80$\tabularnewline
\hline
\end{tabular}\end{center}\label{table:vaccine_cohort}
\end{table}

@@

\vspace{5mm} %5mm vertical space
\begin{table}
% latex table generated in R 3.0.2 by xtable 1.7-3 package
% Fri Mar 20 22:48:21 2015
\begin{tabular}{lrrrrrr}
  \hline
 & Df & Deviance & Resid. Df & Resid. Dev & F & Pr($>$F) \\ 
  \hline
NULL &  &  & 59 & 1532.80 &  &  \\ 
  Age & 4 & 1345.17 & 55 & 187.63 & 204.01 & 0.0000 \\ 
  Ethnicity & 3 & 19.88 & 52 & 167.75 & 4.02 & 0.0141 \\ 
  NZDep & 2 & 17.10 & 50 & 150.65 & 5.19 & 0.0102 \\ 
  Age:Ethnicity & 12 & 80.80 & 38 & 69.85 & 4.09 & 0.0004 \\ 
   \hline
\end{tabular}\caption{Significance of different predictor variables for measles risk factors from 2007-2014, estimated using \autoref{eq:reg} and a quasipoisson error structure}
\label{table:anova}
\end{table}

@@

\vspace{5mm} %5mm vertical space
\begin{table}
% latex table generated in R 3.0.2 by xtable 1.7-3 package
% Fri Mar 20 22:48:21 2015
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std. Error & t value & Pr($>$$|$t$|$) \\ 
  \hline
(Intercept) & -5.9180 & 0.3002 & -19.71 & 0.0000 \\ 
  Age2-4 & -3.3499 & 1.3172 & -2.54 & 0.0152 \\ 
  Age5-17 & -2.2407 & 0.4357 & -5.14 & 0.0000 \\ 
  Age18-24 & -2.7392 & 0.5412 & -5.06 & 0.0000 \\ 
  Age25+ & -2.9353 & 0.3980 & -7.37 & 0.0000 \\ 
  EthnicityEuropean & -0.2464 & 0.3168 & -0.78 & 0.4415 \\ 
  EthnicityMaori & -0.0383 & 0.3433 & -0.11 & 0.9118 \\ 
  EthnicityPacific & 0.9736 & 0.3439 & 2.83 & 0.0074 \\ 
  NZDep4-7 & -0.2609 & 0.0948 & -2.75 & 0.0090 \\ 
  NZDep8-10 & -0.3043 & 0.1040 & -2.93 & 0.0058 \\ 
  Age2-4:EthnicityEuropean & 2.3148 & 1.3319 & 1.74 & 0.0903 \\ 
  Age5-17:EthnicityEuropean & 1.2453 & 0.4566 & 2.73 & 0.0096 \\ 
  Age18-24:EthnicityEuropean & 1.0187 & 0.5743 & 1.77 & 0.0841 \\ 
  Age25+:EthnicityEuropean & -0.2344 & 0.4298 & -0.55 & 0.5887 \\ 
  Age2-4:EthnicityMaori & 2.2135 & 1.3524 & 1.64 & 0.1099 \\ 
  Age5-17:EthnicityMaori & 1.1421 & 0.4844 & 2.36 & 0.0236 \\ 
  Age18-24:EthnicityMaori & 0.4465 & 0.6710 & 0.67 & 0.5098 \\ 
  Age25+:EthnicityMaori & -1.2693 & 0.6285 & -2.02 & 0.0505 \\ 
  Age2-4:EthnicityPacific & 1.3350 & 1.3838 & 0.96 & 0.3408 \\ 
  Age5-17:EthnicityPacific & -0.3256 & 0.5299 & -0.61 & 0.5426 \\ 
  Age18-24:EthnicityPacific & -0.0167 & 0.7113 & -0.02 & 0.9814 \\ 
  Age25+:EthnicityPacific & -0.8973 & 0.5614 & -1.60 & 0.1183 \\ 
   \hline
\end{tabular}\caption{Summary of the regression model results for measles risk factors for cases from 2007-2014}
\label{table:regression_riskfactors}
\end{table}
\vspace{5mm} %5mm vertical space

@@

\begin{figure}
\begin{center}
\includegraphics{draftfinalreport_v2-017}
\end{center}
\caption{Trend in global per capita measles incidence}
\label{fig:trendincidence}
\end{figure}

@@

%latex.default(vacp, file = "", table.env = FALSE, rowname = NULL)%
\begin{center}
\begin{tabular}{lrrrrrrrr}
\hline\hline
\multicolumn{1}{c}{Age range}&\multicolumn{1}{c}{Proportion}&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{NA}\tabularnewline
\hline
Auckland&$ 436350$&$ 52010$&$ 31159$&$ 17920$&$0.34$&$ 34090$&$2$&$ 82$\tabularnewline
Bay of Plenty&$ 206000$&$ 20679$&$  8437$&$  4585$&$0.22$&$ 16094$&$2$&$ 71$\tabularnewline
Canterbury&$ 482180$&$ 51357$&$ 24695$&$ 13687$&$0.27$&$ 37670$&$2$&$ 62$\tabularnewline
Capital and Coast&$ 283700$&$ 32625$&$ 18403$&$ 10461$&$0.32$&$ 22164$&$3$&$ 96$\tabularnewline
Counties Manukau&$ 469300$&$ 55544$&$ 32903$&$ 18880$&$0.34$&$ 36664$&$3$&$ 50$\tabularnewline
Hawke's Bay&$ 151700$&$ 15602$&$  6846$&$  3751$&$0.24$&$ 11851$&$2$&$ 56$\tabularnewline
Hutt Valley&$ 138380$&$ 15198$&$  7836$&$  4388$&$0.29$&$ 10810$&$2$&$ 86$\tabularnewline
Lakes&$  98196$&$ 10558$&$  5192$&$  2886$&$0.27$&$  7672$&$2$&$ 62$\tabularnewline
MidCentral&$ 162560$&$ 17328$&$  8348$&$  4628$&$0.27$&$ 12700$&$2$&$ 75$\tabularnewline
Nelson Marlborough&$ 137000$&$ 13059$&$  4411$&$  2356$&$0.18$&$ 10703$&$3$&$ 90$\tabularnewline
Northland&$ 151690$&$ 14921$&$  5688$&$  3071$&$0.21$&$ 11850$&$3$&$ 70$\tabularnewline
South Canterbury&$  55620$&$  5238$&$  1678$&$   893$&$0.17$&$  4345$&$3$&$ 72$\tabularnewline
Southern&$ 297420$&$ 31607$&$ 15115$&$  8371$&$0.26$&$ 23236$&$2$&$102$\tabularnewline
Tairawhiti&$  43650$&$  4769$&$  2431$&$  1359$&$0.28$&$  3410$&$2$&$ 47$\tabularnewline
Taranaki&$ 109750$&$ 11473$&$  5262$&$  2899$&$0.25$&$  8574$&$3$&$ 68$\tabularnewline
Waikato&$ 359310$&$ 39402$&$ 20248$&$ 11331$&$0.29$&$ 28071$&$2$&$ 95$\tabularnewline
Wairarapa&$  41112$&$  3932$&$  1346$&$   720$&$0.18$&$  3212$&$3$&$ 59$\tabularnewline
Waitemata&$ 525550$&$ 58350$&$ 30774$&$ 17291$&$0.30$&$ 41059$&$2$&$ 70$\tabularnewline
West Coast&$  32151$&$  3197$&$  1265$&$   685$&$0.21$&$  2512$&$2$&$ 50$\tabularnewline
Whanganui&$  60120$&$  6075$&$  2530$&$  1378$&$0.23$&$  4697$&$2$&$ 58$\tabularnewline
Total&$4241739$&$462924$&$234567$&$131540$&$0.28$&$331384$&$2$&$106$\tabularnewline
\hline
\end{tabular}\end{center}\label{table:vacp}
\end{sidewaystable}

@@

\begin{sidewaystable}\small
\caption{Benefit--cost analyses with 20 dollars per vaccine. \textit{Vacc} is numbers to vaccinate (see \autoref{table:attack}); \textit{Vacc costs} is cost for the catch up vaccination programme; \textit{Wages saved} is wages of care givers and cases saved (\$839 per case); \textit{Contacts} is costs saved through contact exclusion; \textit{Manage saved} is management costs saved (\$1,765 per case); \textit{Hosp saved} is the hospitalisation costs saved (\$1,877 per case); \textit{Costs save}	is the discounted costs saved; \textit{Outbreak}	is the predicted outbreak size despite $R_v < 1$ due to measles importation from 1000 simulations; \textit{OB costs}	is costs expected due to continued measles importations based on 10 introdcutions of measles, one per year, but costs discounted on the same discounted rate; \textit{B/C} is the benefit--cost ratio.}
%latex.default(costtable20, file = "", table.env = FALSE, rowname = NULL)%
\begin{tabular}{lrrrrrrrrrr}
\multicolumn{1}{c}{DHB}&\multicolumn{1}{c}{Vacc}&\multicolumn{1}{c}{Vacc costs}&\multicolumn{1}{c}{Wages saved}&\multicolumn{1}{c}{Manage saved}&\multicolumn{1}{c}{Hosp saved}&\multicolumn{1}{c}{Contacts}&\multicolumn{1}{c}{Costs saved}&\multicolumn{1}{c}{Outbreak}&\multicolumn{1}{c}{OB costs}&\multicolumn{1}{c}{B/C}\tabularnewline
Auckland&$17920$&$358400$&$26546458.800$&$55634144.560$&$ 9942525.31$&$81779020.980$&$152792322.900$&$ 82$&$4020979.645$&$34.9$\tabularnewline
Bay of Plenty&$ 4585$&$ 91700$&$ 7188050.737$&$15064195.820$&$ 2692162.33$&$22143509.100$&$ 41371957.640$&$ 71$&$3481579.936$&$11.6$\tabularnewline
Canterbury&$13687$&$273740$&$21039340.160$&$44092724.410$&$ 7879927.55$&$64813791.300$&$121095234.500$&$ 62$&$3040252.902$&$36.5$\tabularnewline
Capital and Coast&$10461$&$209220$&$15678759.950$&$32858408.880$&$ 5872213.27$&$48299987.910$&$ 90241571.220$&$ 96$&$4707488.364$&$18.4$\tabularnewline
Counties Manukau&$18880$&$377600$&$28032290.320$&$58748042.570$&$10499018.27$&$86356273.550$&$161344260.100$&$ 50$&$2451816.857$&$57.0$\tabularnewline
Hawke's Bay&$ 3751$&$ 75020$&$ 5832570.267$&$12223478.090$&$ 2184490.14$&$17967815.970$&$ 33570276.400$&$ 56$&$2746034.879$&$11.9$\tabularnewline
Hutt Valley&$ 4388$&$ 87760$&$ 6676018.202$&$13991115.140$&$ 2500389.24$&$20566141.670$&$ 38424873.780$&$ 86$&$4217124.993$&$ 8.9$\tabularnewline
Lakes&$ 2886$&$ 57720$&$ 4423415.838$&$ 9270274.353$&$ 1656715.28$&$13626774.830$&$ 25459666.240$&$ 62$&$3040252.902$&$ 8.2$\tabularnewline
MidCentral&$ 4628$&$ 92560$&$ 7112225.619$&$14905287.040$&$ 2663763.32$&$21909922.240$&$ 40935534.240$&$ 75$&$3677725.285$&$10.9$\tabularnewline
Nelson Marlborough&$ 2356$&$ 47120$&$ 3758029.134$&$ 7875805.118$&$ 1407505.99$&$11576984.550$&$ 21629928.310$&$ 90$&$4413270.342$&$ 4.8$\tabularnewline
Northland&$ 3071$&$ 61420$&$ 4845991.773$&$10155878.370$&$ 1814983.92$&$14928562.260$&$ 27891868.560$&$ 70$&$3432543.599$&$ 8.0$\tabularnewline
South Canterbury&$  893$&$ 17860$&$ 1429601.652$&$ 2996055.540$&$  535433.02$&$ 4404030.849$&$  8228297.370$&$ 72$&$3530616.273$&$ 2.3$\tabularnewline
Southern&$ 8371$&$167420$&$12877490.450$&$26987711.260$&$ 4823045.35$&$39670397.070$&$ 74118423.570$&$102$&$5001706.387$&$14.3$\tabularnewline
Tairawhiti&$ 1359$&$ 27180$&$ 2071133.263$&$ 4340531.000$&$  775707.79$&$ 6380333.130$&$ 11920733.560$&$ 47$&$2304707.845$&$ 5.1$\tabularnewline
Taranaki&$ 2899$&$ 57980$&$ 4483053.571$&$ 9395258.791$&$ 1679051.58$&$13810494.830$&$ 25802920.600$&$ 68$&$3334470.925$&$ 7.6$\tabularnewline
Waikato&$11331$&$226620$&$17250640.190$&$36152641.580$&$ 6460934.32$&$53142322.180$&$ 99288775.420$&$ 95$&$4658452.027$&$20.3$\tabularnewline
Wairarapa&$  720$&$ 14400$&$ 1146748.405$&$ 2403272.203$&$  429495.14$&$ 3532673.136$&$  6600290.978$&$ 59$&$2893143.891$&$ 2.3$\tabularnewline
Waitemata&$17291$&$345820$&$26218451.270$&$54946730.150$&$ 9819675.66$&$80768560.990$&$150904423.900$&$ 70$&$3432543.599$&$39.9$\tabularnewline
West Coast&$  685$&$ 13700$&$ 1077739.028$&$ 2258647.353$&$  403648.85$&$ 3320082.851$&$  6203096.647$&$ 50$&$2451816.857$&$ 2.5$\tabularnewline
Whanganui&$ 1378$&$ 27560$&$ 2155478.057$&$ 4517294.706$&$  807297.70$&$ 6640165.701$&$ 12406193.290$&$ 58$&$2844107.554$&$ 4.3$\tabularnewline

>>>>

% \begin{table}[hbtp]\scriptsize
% <<results=tex,echo=FALSE>>=# This chunk uses "results=tex"
% latex(ttyr, file="",table.env=FALSE,rowname=NULL)
% @
% \caption{Absolute number of measles cases with no ethnicity recorded for specific age and socio-economic deprivation (NZDep) categories from 2007-2014.}
% \label{table:none}
% \end{table}

@@

% \begin{table}[hbtp]\scriptsize
% \caption{Per capita measles rates}
% <<results=tex,echo=FALSE>>=
% latex(PerCap, file="", table.env=FALSE,rowname=NULL)
% @
% \label{table:percap_rates}
% \end{table}

\begin{table}[hbtp]\footnotesize
\caption{Proportions of the na\"{\i}ve population the would be covered if vaccinated by age groups}
%latex.default(propvCohort, file = "", table.env = FALSE, rowname = NULL)%
\begin{center}
\begin{tabular}{ll}
\hline\hline
\multicolumn{1}{c}{Age range}&\multicolumn{1}{c}{Proportion}\tabularnewline
\hline
2-5&0.04\tabularnewline
5-11&0.15\tabularnewline
5-16&0.27\tabularnewline
5-18&0.31\tabularnewline
11-16&0.14\tabularnewline
11-18&0.18\tabularnewline
0-29&0.72\tabularnewline
0-44&0.89\tabularnewline
\textgreater8&0.8\tabularnewline
\hline
\end{tabular}\end{center}\label{table:vaccine_cohort}
\end{table}

@@

\vspace{5mm} %5mm vertical space
\begin{table}
% latex table generated in R 3.0.2 by xtable 1.7-1 package
% Sun Mar 22 01:29:41 2015
\begin{tabular}{lrrrrrr}
  \hline
 & Df & Deviance & Resid. Df & Resid. Dev & F & Pr($>$F) \\ 
  \hline
NULL &  &  & 59 & 1532.80 &  &  \\ 
  Age & 4 & 1345.17 & 55 & 187.63 & 204.01 & 0.0000 \\ 
  Ethnicity & 3 & 19.88 & 52 & 167.75 & 4.02 & 0.0141 \\ 
  NZDep & 2 & 17.10 & 50 & 150.65 & 5.19 & 0.0102 \\ 
  Age:Ethnicity & 12 & 80.80 & 38 & 69.85 & 4.09 & 0.0004 \\ 
   \hline
\end{tabular}\caption{Significance of different predictor variables for measles risk factors from 2007-2014, estimated using \autoref{eq:reg} and a quasipoisson error structure}
\label{table:anova}
\end{table}

@@

\vspace{5mm} %5mm vertical space
\begin{table}
% latex table generated in R 3.0.2 by xtable 1.7-1 package
% Sun Mar 22 01:29:41 2015
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std. Error & t value & Pr($>$$|$t$|$) \\ 
  \hline
(Intercept) & -6.1644 & 0.1267 & -48.65 & 0.0000 \\ 
  Age2-4 & -1.0351 & 0.1972 & -5.25 & 0.0000 \\ 
  Age5-17 & -0.9954 & 0.1368 & -7.28 & 0.0000 \\ 
  Age18-24 & -1.7204 & 0.1926 & -8.93 & 0.0000 \\ 
  Age25+ & -3.1697 & 0.1622 & -19.55 & 0.0000 \\ 
  EthnicityAsian & 0.2464 & 0.3168 & 0.78 & 0.4415 \\ 
  EthnicityMaori & 0.2081 & 0.2121 & 0.98 & 0.3327 \\ 
  EthnicityPacific & 1.2200 & 0.2134 & 5.72 & 0.0000 \\ 
  NZDep4-7 & -0.2609 & 0.0948 & -2.75 & 0.0090 \\ 
  NZDep8-10 & -0.3043 & 0.1040 & -2.93 & 0.0058 \\ 
  Age2-4:EthnicityAsian & -2.3148 & 1.3319 & -1.74 & 0.0903 \\ 
  Age5-17:EthnicityAsian & -1.2453 & 0.4566 & -2.73 & 0.0096 \\ 
  Age18-24:EthnicityAsian & -1.0187 & 0.5743 & -1.77 & 0.0841 \\ 
  Age25+:EthnicityAsian & 0.2344 & 0.4298 & 0.55 & 0.5887 \\ 
  Age2-4:EthnicityMaori & -0.1013 & 0.3644 & -0.28 & 0.7826 \\ 
  Age5-17:EthnicityMaori & -0.1032 & 0.2521 & -0.41 & 0.6846 \\ 
  Age18-24:EthnicityMaori & -0.5723 & 0.4409 & -1.30 & 0.2022 \\ 
  Age25+:EthnicityMaori & -1.0349 & 0.5127 & -2.02 & 0.0506 \\ 
  Age2-4:EthnicityPacific & -0.9798 & 0.4676 & -2.10 & 0.0429 \\ 
  Age5-17:EthnicityPacific & -1.5709 & 0.3312 & -4.74 & 0.0000 \\ 
  Age18-24:EthnicityPacific & -1.0354 & 0.5003 & -2.07 & 0.0453 \\ 
  Age25+:EthnicityPacific & -0.6629 & 0.4279 & -1.55 & 0.1296 \\ 
   \hline
\end{tabular}\caption{Summary of the regression model results for measles risk factors for cases from 2007-2014}
\label{table:regression_riskfactors}
\end{table}
\vspace{5mm} %5mm vertical space

@@

\begin{figure}
\begin{center}
\includegraphics{draftfinalreport_v2-015}
\end{center}
\caption{Trend in global per capita measles incidence}
\label{fig:trendincidence}
\end{figure}

@@

%latex.default(vacp, file = "", table.env = FALSE, rowname = NULL)%
\begin{center}
\begin{tabular}{lrrrrrrrr}
\hline\hline
\multicolumn{1}{c}{DHB}&\multicolumn{1}{c}{Size}&\multicolumn{1}{c}{Naïve}&\multicolumn{1}{c}{Attack}&\multicolumn{1}{c}{Vacc}&\multicolumn{1}{c}{Proportion}&\multicolumn{1}{c}{Naïve.post.vaccination}&\multicolumn{1}{c}{Median.outbreak}&\multicolumn{1}{c}{Mean.outbreak}\tabularnewline
\hline
Auckland&$ 436350$&$ 52010$&$ 31159$&$ 17920$&$0.34$&$ 34090$&$2$&$ 82$\tabularnewline
Bay of Plenty&$ 206000$&$ 20679$&$  8437$&$  4585$&$0.22$&$ 16094$&$2$&$ 71$\tabularnewline
Canterbury&$ 482180$&$ 51357$&$ 24695$&$ 13687$&$0.27$&$ 37670$&$2$&$ 62$\tabularnewline
Capital and Coast&$ 283700$&$ 32625$&$ 18403$&$ 10461$&$0.32$&$ 22164$&$3$&$ 96$\tabularnewline
Counties Manukau&$ 469300$&$ 55544$&$ 32903$&$ 18880$&$0.34$&$ 36664$&$3$&$ 50$\tabularnewline
Hawke's Bay&$ 151700$&$ 15602$&$  6846$&$  3751$&$0.24$&$ 11851$&$2$&$ 56$\tabularnewline
Hutt Valley&$ 138380$&$ 15198$&$  7836$&$  4388$&$0.29$&$ 10810$&$2$&$ 86$\tabularnewline
Lakes&$  98196$&$ 10558$&$  5192$&$  2886$&$0.27$&$  7672$&$2$&$ 62$\tabularnewline
MidCentral&$ 162560$&$ 17328$&$  8348$&$  4628$&$0.27$&$ 12700$&$2$&$ 75$\tabularnewline
Nelson Marlborough&$ 137000$&$ 13059$&$  4411$&$  2356$&$0.18$&$ 10703$&$3$&$ 90$\tabularnewline
Northland&$ 151690$&$ 14921$&$  5688$&$  3071$&$0.21$&$ 11850$&$3$&$ 70$\tabularnewline
South Canterbury&$  55620$&$  5238$&$  1678$&$   893$&$0.17$&$  4345$&$3$&$ 72$\tabularnewline
Southern&$ 297420$&$ 31607$&$ 15115$&$  8371$&$0.26$&$ 23236$&$2$&$102$\tabularnewline
Tairawhiti&$  43650$&$  4769$&$  2431$&$  1359$&$0.28$&$  3410$&$2$&$ 47$\tabularnewline
Taranaki&$ 109750$&$ 11473$&$  5262$&$  2899$&$0.25$&$  8574$&$3$&$ 68$\tabularnewline
Waikato&$ 359310$&$ 39402$&$ 20248$&$ 11331$&$0.29$&$ 28071$&$2$&$ 95$\tabularnewline
Wairarapa&$  41112$&$  3932$&$  1346$&$   720$&$0.18$&$  3212$&$3$&$ 59$\tabularnewline
Waitemata&$ 525550$&$ 58350$&$ 30774$&$ 17291$&$0.30$&$ 41059$&$2$&$ 70$\tabularnewline
West Coast&$  32151$&$  3197$&$  1265$&$   685$&$0.21$&$  2512$&$2$&$ 50$\tabularnewline
Whanganui&$  60120$&$  6075$&$  2530$&$  1378$&$0.23$&$  4697$&$2$&$ 58$\tabularnewline
Total&$4241739$&$462924$&$234567$&$131540$&$0.28$&$331384$&$2$&$106$\tabularnewline
\hline
\end{tabular}\end{center}\label{table:vacp}
\end{sidewaystable}

@@

\begin{sidewaystable}\small
\caption{Benefit--cost analyses with 20 dollars per vaccine. \textit{Vacc} is numbers to vaccinate (see \autoref{table:attack}); \textit{Vacc costs} is cost for the catch up vaccination programme; \textit{Wages saved} is wages of care givers and cases saved (\$839 per case); \textit{Contacts} is costs saved through contact exclusion; \textit{Manage saved} is management costs saved (\$1,765 per case); \textit{Hosp saved} is the hospitalisation costs saved (\$1,877 per case); \textit{Costs save}	is the discounted costs saved; \textit{Outbreak}	is the predicted outbreak size despite $R_v < 1$ due to measles importation from 1000 simulations; \textit{OB costs}	is costs expected due to continued measles importations based on 10 introdcutions of measles, one per year, but costs discounted on the same discounted rate; \textit{B/C} is the benefit--cost ratio.}
%latex.default(costtable20, file = "", table.env = FALSE, rowname = NULL)%
\begin{center}
\begin{tabular}{lrrrrrrrrrr}
\hline\hline
\multicolumn{1}{c}{DHB}&\multicolumn{1}{c}{Vacc}&\multicolumn{1}{c}{Vacc costs}&\multicolumn{1}{c}{Wages saved}&\multicolumn{1}{c}{Manage saved}&\multicolumn{1}{c}{Hosp saved}&\multicolumn{1}{c}{Contacts}&\multicolumn{1}{c}{Costs saved}&\multicolumn{1}{c}{Outbreak}&\multicolumn{1}{c}{OB costs}&\multicolumn{1}{c}{B/C}\tabularnewline
\hline
Auckland&$17920$&$358400$&$26546459$&$55634145$&$ 9942525$&$81779021$&$152792323$&$ 82$&$4020980$&$34.9$\tabularnewline
Bay of Plenty&$ 4585$&$ 91700$&$ 7188051$&$15064196$&$ 2692162$&$22143509$&$ 41371958$&$ 71$&$3481580$&$11.6$\tabularnewline
Canterbury&$13687$&$273740$&$21039340$&$44092724$&$ 7879928$&$64813791$&$121095235$&$ 62$&$3040253$&$36.5$\tabularnewline
Capital and Coast&$10461$&$209220$&$15678760$&$32858409$&$ 5872213$&$48299988$&$ 90241571$&$ 96$&$4707488$&$18.4$\tabularnewline
Counties Manukau&$18880$&$377600$&$28032290$&$58748043$&$10499018$&$86356274$&$161344260$&$ 50$&$2451817$&$57.0$\tabularnewline
Hawke's Bay&$ 3751$&$ 75020$&$ 5832570$&$12223478$&$ 2184490$&$17967816$&$ 33570276$&$ 56$&$2746035$&$11.9$\tabularnewline
Hutt Valley&$ 4388$&$ 87760$&$ 6676018$&$13991115$&$ 2500389$&$20566142$&$ 38424874$&$ 86$&$4217125$&$ 8.9$\tabularnewline
Lakes&$ 2886$&$ 57720$&$ 4423416$&$ 9270274$&$ 1656715$&$13626775$&$ 25459666$&$ 62$&$3040253$&$ 8.2$\tabularnewline
MidCentral&$ 4628$&$ 92560$&$ 7112226$&$14905287$&$ 2663763$&$21909922$&$ 40935534$&$ 75$&$3677725$&$10.9$\tabularnewline
Nelson Marlborough&$ 2356$&$ 47120$&$ 3758029$&$ 7875805$&$ 1407506$&$11576985$&$ 21629928$&$ 90$&$4413270$&$ 4.8$\tabularnewline
Northland&$ 3071$&$ 61420$&$ 4845992$&$10155878$&$ 1814984$&$14928562$&$ 27891869$&$ 70$&$3432544$&$ 8.0$\tabularnewline
South Canterbury&$  893$&$ 17860$&$ 1429602$&$ 2996056$&$  535433$&$ 4404031$&$  8228297$&$ 72$&$3530616$&$ 2.3$\tabularnewline
Southern&$ 8371$&$167420$&$12877490$&$26987711$&$ 4823045$&$39670397$&$ 74118424$&$102$&$5001706$&$14.3$\tabularnewline
Tairawhiti&$ 1359$&$ 27180$&$ 2071133$&$ 4340531$&$  775708$&$ 6380333$&$ 11920734$&$ 47$&$2304708$&$ 5.1$\tabularnewline
Taranaki&$ 2899$&$ 57980$&$ 4483054$&$ 9395259$&$ 1679052$&$13810495$&$ 25802921$&$ 68$&$3334471$&$ 7.6$\tabularnewline
Waikato&$11331$&$226620$&$17250640$&$36152642$&$ 6460934$&$53142322$&$ 99288775$&$ 95$&$4658452$&$20.3$\tabularnewline
Wairarapa&$  720$&$ 14400$&$ 1146748$&$ 2403272$&$  429495$&$ 3532673$&$  6600291$&$ 59$&$2893144$&$ 2.3$\tabularnewline
Waitemata&$17291$&$345820$&$26218451$&$54946730$&$ 9819676$&$80768561$&$150904424$&$ 70$&$3432544$&$39.9$\tabularnewline
West Coast&$  685$&$ 13700$&$ 1077739$&$ 2258647$&$  403649$&$ 3320083$&$  6203097$&$ 50$&$2451817$&$ 2.5$\tabularnewline
Whanganui&$ 1378$&$ 27560$&$ 2155478$&$ 4517295$&$  807298$&$ 6640166$&$ 12406193$&$ 58$&$2844108$&$ 4.3$\tabularnewline
\hline
\end{tabular}\end{center}\label{table:cost20}
\end{sidewaystable}
